---
title: "Kernel"
author: "leeSunho"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

packages = c('rgdal', 'sf', 'spdep', 'tmap', 'tidyverse', 'maptools', 'raster', 'spatstat','prettydoc','spData')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}

```


```{r}


gym <- readOGR(dsn = "data/geospatial/gymssg/gyms-sg.shp",
          layer = "gyms-sg")

eat <- readOGR(dsn = "data/geospatial/healthier-eateries/healthier-eateries.shp",
          layer = "healthier-eateries")

places <- readOGR(dsn = "data/geospatial/Singapore-shp/shape/places.shp",
          layer = "places")



sg <- readOGR(dsn = "data/geospatial/coastal-outline", layer="CostalOutline")



```
1. GYM
```{r}
sg_sp <- as(sg, "SpatialPolygons")
sg_owin <- as(sg_sp, "owin")

gym_sp <- as(gym, "SpatialPoints")
gym_ppp <- as(gym_sp, "ppp")
gym_ppp <- rjitter(gym_ppp, retry=TRUE, nsim=1, drop=TRUE)
gymSG_ppp <- gym_ppp[sg_owin]

```

```{r}

plot(gymSG_ppp)

```
Kernel Density Maps
```{r}

gymSG_ppp.bw <- density(gymSG_ppp, sigma=bw.diggle, edge=TRUE, kernel="gaussian")
plot(gymSG_ppp.bw)

```

```{r}

gymSG_ppp.km <- rescale(gymSG_ppp, 1000, "km")

```
Convert KDE output into grid object
```{r}


kde_gymSG.bw <- density(gymSG_ppp.km, sigma=bw.diggle, edge=TRUE, kernel="gaussian")

kde_gymSG.ppl <- density(gymSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="gaussian")

par(mfrow=c(1,2))
plot(kde_gymSG.bw, main = "bw.diggle")
plot(kde_gymSG.ppl, main = "bw.ppl")

```

```{r}
par(mfrow=c(1,2))
plot(density(gymSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="gaussian"), main="Gaussian")
plot(density(gymSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="epanechnikov"), main="Epanechnikov")


```

```{r}
par(mfrow=c(1,2))
plot(density(gymSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="quartic"), main="Quartic")
plot(density(gymSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="disc"), main="Disc")


```
Computing kernel density estimation by defining bandwidth manually

```{r}

kde_gymSG_600 <- density(gymSG_ppp.km, sigma=0.6, edge=TRUE, kernel="gaussian")
plot(kde_gymSG_600)

```
Computing kernel density estimation by using adaptive bandwidth
```{r}

kde_gymSG_adaptive <- adaptive.density(gymSG_ppp.km, method="kernel")
plot(kde_gymSG_adaptive)

```
```{r}
par(mfrow=c(1,2))
plot(kde_gymSG.bw, main = "Fixed bandwidth")
plot(kde_gymSG_adaptive, main = "Adaptive bandwidth")

```
Converting KDE output into grid object.
```{r}
gridded_kde_gymSG_bw <- as.SpatialGridDataFrame.im(kde_gymSG.bw)
spplot(gridded_kde_gymSG_bw)

```

Converting gridded output into raster
```{r}
kde_gymSG_bw_raster <- raster(gridded_kde_gymSG_bw)
projection(kde_gymSG_bw_raster) <- CRS("+init=EPSG:3414")

```

```{r}
tm_shape(kde_gymSG_bw_raster) + 
  tm_raster("v") +
  tm_layout(legend.position = c("right", "bottom"), frame = FALSE)

```


2.Healthier eateries
```{r}
#filter the fastfood
eat_sp <- as(eat, "SpatialPoints")
#eat <- eat_sp %>%
#  filter(!grepl("McDonald"), Name)

```

```{r}
sg_sp <- as(sg, "SpatialPolygons")
sg_owin <- as(sg_sp, "owin")

eat_sp <- as(eat, "SpatialPoints")
eat_ppp <- as(eat_sp, "ppp")
eat_ppp <- rjitter(eat_ppp, retry=TRUE, nsim=1, drop=TRUE)
eatSG_ppp <- eat_ppp[sg_owin]

```

```{r}

plot(eatSG_ppp)

```
Kernel Density Maps
```{r}

eatSG_ppp.bw <- density(eatSG_ppp, sigma=bw.diggle, edge=TRUE, kernel="gaussian")
plot(eatSG_ppp.bw)

```

```{r}

eatSG_ppp.km <- rescale(eatSG_ppp, 1000, "km")

```
Convert KDE output into grid object
```{r}


kde_eatSG.bw <- density(eatSG_ppp.km, sigma=bw.diggle, edge=TRUE, kernel="gaussian")

kde_eatSG.ppl <- density(eatSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="gaussian")

par(mfrow=c(1,2))
plot(kde_eatSG.bw, main = "bw.diggle")
plot(kde_eatSG.ppl, main = "bw.ppl")

```

```{r}
par(mfrow=c(1,2))
plot(density(eatSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="gaussian"), main="Gaussian")
plot(density(eatSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="epanechnikov"), main="Epanechnikov")


```

```{r}
par(mfrow=c(1,2))
plot(density(eatSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="quartic"), main="Quartic")
plot(density(eatSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="disc"), main="Disc")


```
Computing kernel density estimation by defining bandwidth manually

```{r}

kde_eatSG_600 <- density(eatSG_ppp.km, sigma=0.6, edge=TRUE, kernel="gaussian")
plot(kde_eatSG_600)

```
Computing kernel density estimation by using adaptive bandwidth
```{r}

kde_eatSG_adaptive <- adaptive.density(eatSG_ppp.km, method="kernel")
plot(kde_eatSG_adaptive)

```



```{r}
par(mfrow=c(1,2))
plot(kde_eatSG.bw, main = "Fixed bandwidth")
plot(kde_eatSG_adaptive, main = "Adaptive bandwidth")

```
Converting KDE output into grid object.
```{r}
gridded_kde_eatSG_bw <- as.SpatialGridDataFrame.im(kde_eatSG.bw)
spplot(gridded_kde_eatSG_bw)

```

Converting gridded output into raster
```{r}
kde_eatSG_bw_raster <- raster(gridded_kde_eatSG_bw)
projection(kde_eatSG_bw_raster) <- CRS("+init=EPSG:3414")

```

```{r}
tm_shape(kde_eatSG_bw_raster) + 
  tm_raster("v") +
  tm_layout(legend.position = c("right", "bottom"), frame = FALSE)

```


3.places series


```{r}
sg_sp <- as(sg, "SpatialPolygons")
sg_owin <- as(sg_sp, "owin")

places_sp <- SpatialPoints(places)

#places_sp <- as(places, "Spatialplacess")
places_ppp <- as(places_sp, "ppp")
places_ppp <- rjitter(places_ppp, retry=TRUE, nsim=1, drop=TRUE)
placesSG_ppp <- places_ppp[sg_owin]

```

```{r}

plot(placesSG_ppp)

```
Kernel Density Maps
```{r}

placesSG_ppp.bw <- density(placesSG_ppp, sigma=bw.diggle, edge=TRUE, kernel="gaussian")
plot(placesSG_ppp.bw)

```

```{r}

placesSG_ppp.km <- rescale(placesSG_ppp, 1000, "km")

```
Convert KDE output into grid object
```{r}


kde_placesSG.bw <- density(placesSG_ppp.km, sigma=bw.diggle, edge=TRUE, kernel="gaussian")

kde_placesSG.ppl <- density(placesSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="gaussian")

par(mfrow=c(1,2))
plot(kde_placesSG.bw, main = "bw.diggle")
plot(kde_placesSG.ppl, main = "bw.ppl")

```

```{r}
par(mfrow=c(1,2))
plot(density(placesSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="gaussian"), main="Gaussian")
plot(density(placesSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="epanechnikov"), main="Epanechnikov")


```

```{r}
par(mfrow=c(1,2))
plot(density(placesSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="quartic"), main="Quartic")
plot(density(placesSG_ppp.km, sigma=bw.ppl, edge=TRUE, kernel="disc"), main="Disc")


```
Computing kernel density estimation by defining bandwidth manually

```{r}

kde_placesSG_600 <- density(placesSG_ppp.km, sigma=0.6, edge=TRUE, kernel="gaussian")
plot(kde_placesSG_600)

```
Computing kernel density estimation by using adaptive bandwidth
```{r}

kde_placesSG_adaptive <- adaptive.density(placesSG_ppp.km, method="kernel")
plot(kde_placesSG_adaptive)

```


```{r}
par(mfrow=c(1,2))
plot(kde_placesSG.bw, main = "Fixed bandwidth")
plot(kde_placesSG_adaptive, main = "Adaptive bandwidth")

```
Converting KDE output into grid object.
```{r}
gridded_kde_placesSG_bw <- as.SpatialGridDataFrame.im(kde_placesSG.bw)
spplot(gridded_kde_placesSG_bw)

```

Converting gridded output into raster
```{r}
kde_placesSG_bw_raster <- raster(gridded_kde_placesSG_bw)
projection(kde_placesSG_bw_raster) <- CRS("+init=EPSG:3414")

```

```{r}
tm_shape(kde_placesSG_bw_raster) + 
  tm_raster("v") +
  tm_layout(legend.position = c("right", "bottom"), frame = FALSE)

```
```